### 2021-07-08 rad-icfp-2021/complexity.tex
minor

We define the nesting of array operations $\NestA$ of a term !e! of Source by induction on !e! as follows.

\begin{tabular}{r c l}
    $\NestA$(!c!) &=& 0 \\
    $\NestA$(!x!) &=& 0 \\
    $\NestA$(!let x:A = e$_1$ in e$_2$:B!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!)  \\ 
    $\NestA$(!< e$_1$, e$_2$ >:AxB!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!) \\ 
    $\NestA$($\pi_i$(!e!)) &=& $\NestA$(!e!)\\
    $\NestA$(!e$_1$ op2 e$_2$!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!)\\
    $\NestA$(!op1 e!) &=& $\NestA$(!e!) \\
    $\NestA$(!map2 (x,y.e$_1$) e$_2$ e$_3$!) &=& max 1+$\NestA$(!e$_1$!),$\NestA$(!e$_2$!),$\NestA$(!e$_3$!) \\
    $\NestA$($\Gamma\vdash $ !reduce (x,y.e$_1$) e$_2$ e$_3$!) &=& max 1+$\NestA$(!e$_1$!),$\NestA$(!e$_2$!),$\NestA$(!e$_3$!) \\
\end{tabular}

>>>>

We define the Nesting of Array Operations $\NestA$ of a term !e! of Source by induction on !e! as follows.

\begin{tabular}{r c l}
    $\NestA$(!c!) &=& 0 \\
    $\NestA$(!x!) &=& 0 \\
    $\NestA$(!let x:A = e$_1$ in e$_2$:B!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!)  \\ 
    $\NestA$(!< e$_1$, e$_2$ >:AxB!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!) \\ 
    $\NestA$($\pi_i$(!e!)) &=& $\NestA$(!e!)\\
    $\NestA$(!e$_1$ op2 e$_2$!) &=& max $\NestA$(!e$_1$!), $\NestA$(!e$_2$!)\\
    $\NestA$(!op1 e!) &=& $\NestA$(!e!) \\
    $\NestA$(!map2 (x,y.e$_1$) e$_2$ e$_3$!) &=& max 1+$\NestA$(!e$_1$!),$\NestA$(!e$_2$!),$\NestA$(!e$_3$!) \\
    $\NestA$(!reduce (x,y.e$_1$) e$_2$ e$_3$!) &=& max 1+$\NestA$(!e$_1$!),$\NestA$(!e$_2$!),$\NestA$(!e$_3$!) \\
\end{tabular}
